---
title: "Matching Voter Precincts to Census Block Data"
author: "Calum You"
date: "21st February, 2018"
output:
  html_notebook:
    highlight: tango
    mathjax: null
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float: yes
---

# Introduction
This is a notebook to document the combining of Texas census block data with voting data. The goal is to have a dataset with observations as disaggregated as possible that relates voting history to demographic variables as a source for prediction.

# Setup
Load required packages
```{r setup}
library(tidyverse)
library(sf)
library(magrittr)
```

# Exploration
Input and look at the available data to see what we have.
We have:

* Precinct shapefiles - boundaries on which vote shares are reported.
* Voting district shapefiles - some kind of method of matching precincts to census blocks.
```{r input}
precinct <- st_read(here::here("data", "Precincts", "Precincts.shp"))
vtds <- st_read(here::here("data", "VTDs", "VTDs.shp"))
```

# Harris County
Focus on Harris County since it contains most of the Houston area. Filter the 

```{r harris_shp}
harris_p <- precinct %>% filter(CNTY == 201)
harris_v <- vtds %>% filter(CNTY == 201)
plot(harris_p$geometry)
```

```{r harris_vtr}
load_harris <- function(){
  csvs <- here::here("data", "Harris_County", "All HC Voters") %>%
    list.files(full.names = TRUE) %>%
    map(read_csv, col_types = "ccicccccccic")
  # nobs <- map_int(csvs, nrow)
  ncongr <- c(02, 07, 08, 09, 10, 18, 22, 29)
  for (i in length(csvs)){
    nobs
    csvs[[i]]$congr <- ncongr[1]
  }
  out <- bind_rows(csvs)
}
hc <- load_harris()
hc_tidy <- hc %>%
  set_colnames(str_to_lower(colnames(.))) %>%
  set_colnames(str_replace())

write_rds(hc, here::here("data", "Harris_County", "all_voters.rds"), compress = "xz")

```

