---
title: "Matching Voter Precincts to Census Block Data"
author: "Calum You"
date: "21st February, 2018"
output:
  html_notebook:
    highlight: tango
    mathjax: null
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float: yes
---

# Introduction
This is a notebook to document the combining of Texas census block data with voting data. The goal is to have a dataset with observations as disaggregated as possible that relates voting history to demographic variables as a source for prediction.

# Setup
Load required packages
```{r setup}
library(tidyverse)
library(sf)
library(magrittr)
```

# Exploration
Input and look at the available data to see what we have.
We have:

* Precinct shapefiles - boundaries on which vote shares are reported.
* Voting district shapefiles - some kind of method of matching precincts to census blocks.
```{r input}
precinct <- st_read(here::here("data", "Precincts", "Precincts.shp"))
vtds <- st_read(here::here("data", "VTDs", "VTDs.shp"))
```


